Flow categories originally emerged as a categorical bookkeeping mechanism to organize the geometric and analytic data extracted from Hamiltonian systems on a manifold \cite{CJS95}. In recent years, flow categories and their stable homotopy types have become central tools for lifting invariants in Floer, contact, and Khovanov homology into the realm of stable homotopy theory. A natural question arises: how can we systematically compute the generalized homology of these realization spectra directly from the underlying geometric flow data?   

Here is an intuitive description of the main theorem of the paper using a toy model coming from Morse theory.
Let $\Man$ be a closed manifold and $f: \Man \to \bbR$ a Smale Morse function. Denote by $\mathrm{Crit}(f)$ the set of critical points of $f$, and by $\ind: \mathrm{Crit}(f) \to \bbZ$ the index function. For simplicity, assume that there is one critical point for each index $i \in \{0, \dots, n\}$, and denote the critical points by $x_i$ where $\ind(x_i) = i$.
The first result is:

There is a spectral sequence 
\begin{equation*}
    \pg{E}{1}{n}{p} = \Omega^{\fr}_{n-p} \implies \pi_n \Sinf \Man.
\end{equation*}
where $\Omega^{\fr}_*$ is the framed bordism ring, and $\Sinf \Man$ is the stable homotopy type of  $\Man$.

Let $x_j,x_i$ be two critical points of $f$ with $j > i$. We denote by $\flowM(x_j,x_i)$ the compactification of the moduli space of flow lines from $x_j$ to $x_i$, up to reparametrization. Recall that $\flowM(x_j,x_i)$ is a framed manifold with corners of dimension $\ind(x_j) - \ind(x_i) - 1$, and that the boundary structure is given by
\begin{equation*}
    \partial \flowM(x_j,x_i) = \bigcup_{j > r > i} \flowM(x_j,x_r) \times \flowM(x_r,x_i).
\end{equation*}

Let $W_p$ be a representative of a bordism class in $\pg{E}{1}{n}{p} = \Omega^{\fr}_{n-p}$.
In our framework, we view $W_p$ as a right flow module of degree $n$ over the trivial subcategory containing only the critical point $x_p$.
The main theorem states that $W_p$ survives to the $(r+1)$-th page (also denoted by $W_p \in Z_{r+1}$) if and only if it **extends to a right flow module** $W$ of degree $n$ over the truncated flow category $\fC_{[p, p-r]}$.
Concretely, this means providing a family of framed manifolds $\{W_s\}$ for $s \in \{p, \dots, p-r\}$ of dimension $n-s$ such that the corner structure maps
\begin{equation*}
    W_t \times \flowM(x_t,x_s) \hookrightarrow W_s
\end{equation*}
satisfy the axioms of a right flow module.

To compute the differential, we glue this right module $W$ together with the canonical left flow module $\flowM(-,x_{p-(r+1)})$.
Let $t,u \in \bbZ$ be such that $p \geq t > u \geq p-(r+1)$. By the boundary structure axioms of the right module $W$ and the left module $\flowM(-,x_{p-(r+1)})$, we have the following two embeddings:
\begin{equation*}
    W_t \times \flowM(x_t,x_{p-(r+1)}) \hookleftarrow W_t \times \flowM(x_t,x_u) \times \flowM(x_u,x_{p-(r+1)}) \hookrightarrow W_u \times \flowM(x_u,x_{p-(r+1)})
\end{equation*}
and these boundary components are shared only by these two manifolds of the collection $W_s \times \flowM(x_s,x_{p-(r+1)})$.
Because all boundary components of $W_s \times \flowM(x_s,x_{p-(r+1)})$ are of this form, we can glue the collection together along these shared faces to obtain a framed closed manifold. We denote this closed manifold by $W \circ \flowM(-,x_{p-(r+1)})$, and call it a Toda manifold:
\begin{equation*}
    W \circ \flowM(-,x_{p-(r+1)}) \coloneqq \bigcup_{s \in \{p,\dots, p-r\}} W_s \times \flowM(x_s,x_{p-(r+1)}).
\end{equation*}
This gluing operation is a geometric realization of the composition of modules (sometimes called a geometric tensor product).

To verify that this manifold represents a class in the correct group for the differential, we compute its dimension. For each $s$, the pieces being glued have dimension: 
\begin{equation*}
    \dim(W_s \times \flowM(x_s,x_{p-(r+1)})) = \dim(W_s) + \dim(\flowM(x_s,x_{p-(r+1)})) = (n-s) + \big(s - (p-(r+1)) - 1 \big) = n-p+r.
\end{equation*}
Note that the $-1$ in the second term arises from the dimension formula for flow manifolds. The result $n-p+r$ matches the expected dimension for an element of the $(r+1)$-th page.
The last part of the theorem states that if $W_p$ survives to $Z_{r+1}$, then the $r+1$ differential is given by the bordism class of this Toda manifold: 
\begin{equation*}
    d_{r+1}(W_p) = [W \circ \flowM(-,x_{p-(r+1)})] \in \Omega^{\fr}_{n-p+r} = \pg{E}{r+1}{n-1}{p-(r+1)}.
\end{equation*}
See \cref{fig:ffCat} for an example of the structure of the right module $W$ and the flow manifolds,
\cref{fig:k-boundary} for the gluing diagram of the Toda manifold, and \cref{fig:differential} for the resulting closed manifold.
